### 2019-03-20 papers/journal/encoding.tex
First push for SMT QBF overlap

\subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
%
We need the following constraints~\eqref{eq:f0} and~\eqref{eq:c3}
to encode the basic structure of VTSs.
%
For an edge to exist it should have one molecule present. 
%
\begin{align}
  \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}\tag{V1}\label{eq:f0}
\end{align}
If a molecule is active on an edge, it should be present on the edge.
%
\begin{align}
  \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\tag{V2}\label{eq:f1}
\end{align}
A molecule should be present to be active on a node.  
\begin{align}
  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
  \tag{V3}\label{eq:c4}
\end{align}
The edge labels are subset of the node labels of the source and target nodes.
\begin{align}
  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )\tag{V4}\label{eq:c0}
\end{align}
Self edges are not allowed. 
\begin{align}
   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V5}\label{eq:c2}
\end{align}
We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of Q-SNAREs to Q-SNAREs (and similarly R-SNAREs to R-SNAREs) in the pairing matrix to be 0's.
%It reduces the search space.
% Condition on $p_{kk'}$. \ashu{why???} .
%\begin{align}
%  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
%  \tag{V6}\label{eq:c3}
%\end{align}

\begin{align}
  \bigwedge\limits_{(x < 3M/4 \, \land  \, y < 3M/4) \lor  (x >= 3M/4 \, \land \, y >= 3M/4)} \neg p(x,y)
  \tag{V6}\label{eq:c3}
\end{align}

\subsubsection{Well-fused constraints}
Constraint~\eqref{eq:fuse1} encodes that each edge must fuse with
its destination node.
%
Constraint~\eqref{eq:fuse2} encodes that each edge should not
be able to potentially fuse with any node other than its destination node.
\begin{align}
  \bigwedge\limits_{i,j,q} e_{i,j,q} \limplies 
\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land
\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land
  \notag \\
	\qquad \qquad \qquad \qquad
	\Lor\limits_{l=1}^4 a_{j,m_l} \land p_{\{m_1,m_2,m_3,m_4\}})
  \tag{V7}\label{eq:fuse1}  
\end{align}

\begin{align}
	\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies
\mspace{300mu}
  \notag \\
	\qquad \qquad \qquad \qquad
	\neg
\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
\mspace{50mu}
  \tag{V8}\label{eq:fuse2}  
\end{align}

@@

\subsubsection{Regulation on nodes and edges}
We are considering several models that differ in constraints on
the activity of molecules.
%
We will present~\eqref{eq:ann}-~\eqref{eq:aep} that encodes
the varying constraints.
%
The following constraint encodes no conditions on activities on nodes,
i.e., all the present molecules on the nodes are active.
\begin{align}
\bigwedge\limits_{i,m} n_{i,m} = a_{i,m}    \tag{Ann}\label{eq:ann}
\end{align}
The following constraint encodes that activity of a molecule $m$ on the node is
defined by a Boolean function $\nodef_m$ of presence of molecules present on that node.
\begin{align}
\bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
\tag{Anb}\label{eq:anb}
\end{align}
The following constraint encodes no conditions on activities on edges,
i.e., all the present molecules on the edges are active.
\begin{align}
  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
\tag{Aen}\label{eq:aen}
\end{align}
The following constraint encodes that activity of a molecule $m$ on the edge is
defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
\begin{align}
   \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
  \tag{Aeb}\label{eq:aeb}
\end{align}
%
The following constraint encodes that the activity of the molecules on
edges is defined by inhibition by other molecules based on the pairing
matrix. 
\begin{align}
	\bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \land \bigwedge_{m_l \neq m,l \in \{1,..,3\}} e_{i,j,q,m'} \land p_{m, m_l}] \limplies 
	\notag \\
	  \qquad \qquad \qquad \qquad
	(\neg b_{i,j,q,m} \land \bigwedge_{\mathclap{m_l \neq m,l, p_{m, m_l} \in \{1,..,3\}}} \neg b_{i,j,q,m_l})
  \tag{Aep}\label{eq:aep}
\end{align}
%
\subsubsection{Constraints for stability condition}
%
We use $m$-reachability to encode the stability condition in VTSs.
%
The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps
if either there is a direct edge between $i$ and $j$ with $m$ present on the edge or there is a edge between $i^{\prime \prime}$ and
$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
\begin{align}
  \bigwedge\limits_{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
  \tag{R1}\label{eq:reach1}
\end{align}
Now we can encode stability using the reachability variables.
and say if there is an $m$-edge between $i$ and $j$, there is
$m$-reachable path from $j$ to $i$.
\begin{align}
 \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
  \tag{R2}\label{eq:reach2}
\end{align}

@@

\subsubsection{$k$-connectivity constraints}
To check whether $k$-connected is a necessary condition, we remove (drop) $k-1$ edges from the graph and if it
disconnects the graph, and we get an assignment. We have a graph that is not  $k$-connected.
%
Constraints~\ref{eq:drop1}-\ref{eq:drop4}
encode the relevant constraints for reachability
in the modified VTS. 
%
The following constraints encode that only
existing edges can be dropped and exactly $k-1$ edges are dropped.
\begin{align}
  \bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \tag{D1}\label{eq:drop1}\\
  \sum_{i,j,q} d_{i,j,q} = k-1
  \tag{D2}\label{eq:drop2}
\end{align}
We need to define reachability in the modified VTS, therefore we use
a new variable $r'_{i,j}$ to encode reachability from $i$ to $j$.
In the following constraint, we encode $r'_{i,j}$ is true if there is an
edge $(i,\_,j)$ and it is not dropped, or there is a node
$i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
not dropped and $r'_{i',j}$ is true.
\begin{align}
\bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}  
  \tag{D3}\label{eq:drop3}
\end{align}
Since we search for disconnected modified VTS,
the following constraint encodes that there are 
unreachable pair of nodes in the underlying undirected graph.
% nodes such that
% there is no path between them .
\begin{align}
   \bigvee\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
  \tag{D4}\label{eq:drop4}
\end{align}

@@

To specify the stability condition, we use nondeterminism to perform enumeration.
%
%Nondeterminism can be viewed as an oracle that guesses a correct path for a specific $m$ if it exists. 
%
%We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
%
%
Note that the enumeration is done only for an unwinding depth $w$.
%
The encoding presented below is a simpler version of the implementation. 
\subsubsection{Constraints for stability condition}
%
A path between node $i$ and $j$ in the graph is a $m$-$path_{ij}$, if molecule $m$ is present on edges along that path.
%
%We use {\npath} to represent the required path to encode the stability condition in VTS.
%
%A naive implementation is shown in~\ref{eq:reachbmc1} where 
We use {\npath}$(m, i, j, w)$ to represent the presence of a $m$-$path_{ij}$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and01
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
The~\ref{eq:reachbmc1} performs enumeration of every $m$-$path_{ij}$ of at most $w$ length. 
%
Starting with exploring $m$-${paths}_{ij}$ of length 1; a direct edge between $i$ and $j$ with molecule $m$ present, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.

@@

\begin{align}
\npath(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} (\texttt{Length} (m-path_{ij}) == l)
  \tag{S1}\label{eq:reachbmc1}
\end{align}

@@

\begin{align}
	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) == 1) \limplies \npath(m, j, i, w)
  \tag{S2}\label{eq:reachbmc2}
\end{align}

>>>>

\subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
%
We need the following constraints \texttt{EdgeC},
\texttt{ActivityC} and \texttt{PairingC} to encode the basic structure of VTSs.
%
For an edge to exist it should have one molecule present. 
%
\begin{align*}
  \texttt{PresentEdge} = \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}
\end{align*}
The edge labels are subset of the node labels of the source and target nodes.
\begin{align*}
  \texttt{LabelEdge} = \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )
\end{align*}
Self edges are not allowed. 
\begin{align*}
  \texttt{SelfEdge} = \bigwedge\limits_{i,q} \neg e_{i,i,q}
\end{align*}

We use \texttt{EdgeC} to collect all the edge related constraints. 
%
\texttt{EdgeC} states that each edge has at least one molecule,
 edge labels are consistent with node labels and there are no self loops.    
\begin{align*}
  \texttt{EdgeC} = \texttt{PresentEdge} \land \texttt{SelfEdge} \land \texttt{LabelEdge} 
\end{align*}

If a molecule is active on an edge, it should be present on the edge.
%
\begin{align*}
  \texttt{ActivityMol} = \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\label{eq:f1}
\end{align*}
A molecule should be present to be active on a node.  
\begin{align*}
    \texttt{PresentMol} = \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
\end{align*}

We use \texttt{ActivityC} to collect all the molecule activity related constraints. 
\texttt{ActivityC} states that active molecule are present.
\begin{align*}
  \texttt{ActivityC} = \texttt{ActivityMol} \land \texttt{PresentMol} 
\end{align*}

We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of Q-SNAREs to Q-SNAREs (and similarly R-SNAREs to R-SNAREs) in the pairing matrix to be 0's.
%It reduces the search space.
% Condition on $p_{kk'}$. \ashu{why???} .
%\begin{align}
%  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
%  \tag{V6}\label{eq:c3}
%\end{align}

\begin{align*}
 \texttt{PairingC} =\;& \bigwedge\limits_{(x < 3M/4 \, \land  \, y < 3M/4) \lor  (x >= 3M/4 \, \land \, y >= 3M/4)} \neg p(x,y)
\end{align*}

\subsubsection{Well-fused constraints}
Constraint \texttt{Fusion1} encodes that each edge must fuse with
its destination node.
%
Constraint \texttt{Fusion2} encodes that each edge should not
be able to potentially fuse with any node other than its destination node.
\begin{align*}
\texttt{Fusion1} =\;&
\bigwedge\limits_{i,j,q} e_{i,j,q} \limplies
\bigvee_{{m_1,m_2,m_3,m_4}} (\Land_{l=1}^4 ( b_{i,j,q,m_l} \lor a_{j,m_l} ) \land 
\Lor\limits_{l=1}^4 b_{i,j,q,m_l} \land\\
& \qquad \qquad \qquad \qquad \Lor\limits_{l=1}^4 a_{j,m_l}\land p_{\{m_1,m_2,m_3,m_4\}})
\\
\texttt{Fusion2} =\;&
\bigwedge\limits_{\mathclap{i,j,q,m_1,m_2,m_3, l \in \{1,..,3\}}} b_{i,j,q,m_1} \land ..\land b_{i,j,q,m_l} \limplies \\
& \hspace{2cm} \neg 
\bigvee_{\mathclap{j \neq j^{\prime}, m_{l+1}^{\prime},..,m_{4}^{\prime}}} ( a_{j^{\prime},m_{l+1}^{\prime}} \land .. \land a_{j^{\prime},m_4^{\prime}} \land p_{\{m_1,..,m_l,m^{\prime}_{l+1},..,m^{\prime}_4\}})
\\
\end{align*}

@@

\subsubsection{Regulation on nodes and edges (Activity function)}
We are considering several models that differ in constraints on
the activity of molecules.
%
%We will present~\eqref{eq:ann}-~\eqref{eq:aep} that encodes
%the varying constraints.
%
The activity of the molecules are controlled by activity functions.
%
We will have encoded five variation of the boolean functions based on the biological discussion.
%
The concrete functions encoding is presented below.
%
We will use \texttt{NodeFun}$_m$ and \texttt{EdgeFun}$_m$ for node and edge regulations respectively.

The following constraint encodes no conditions on activities on nodes,
i.e., all the present molecules on the nodes are active.
\begin{align*}
\texttt{NodeFunOn} =& \bigwedge\limits_{i,m} n_{i,m} = a_{i,m}  
\end{align*}
The following constraint encodes that activity of a molecule $m$ on the node is
defined by a Boolean function $\nodef_m$ of presence of molecules present on that node.
\begin{align*}
\texttt{NodeFunBf} =& \bigwedge\limits_{i,m} n_{i,m} \limplies a_{i,m} =  \nodef_m (n_{i,1},\dots,n_{i,\mu}) 
\end{align*}
The following constraint encodes no conditions on activities on edges,
i.e., all the present molecules on the edges are active.
\begin{align*}
 \texttt{EdgeFunOn} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} = b_{i,j,q,m}
\end{align*}
The following constraint encodes that activity of a molecule $m$ on the edge is
defined by a Boolean function $\edgef_m$ of presence of molecules present on that edge.
\begin{align*}
 \texttt{EdgeFunBf} =& \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies b_{i,j,q,m} = \edgef_k(e_{i,j,q,1}, .., e_{i,j,q,\mu} )
\end{align*}
%
The following constraint encodes that the activity of the molecules on
edges is defined by inhibition by other molecules based on the pairing
matrix. 
\begin{align*}
\texttt{EdgeFunPairing} =&	
\bigwedge\limits_{i,j,q, m}  [e_{i,j,q,m} \land   \\
      \bigwedge_{m_l \neq m,l \in \{1,..,3\}} e_{i,j,q,m'} \land p_{m, m_l}] \limplies 
	(\neg b_{i,j,q,m} \land \bigwedge_{\mathclap{m_l \neq m,l, p_{m, m_l} \in \{1,..,3\}}} \neg b_{i,j,q,m_l})
\end{align*}
%
\subsubsection{Constraints for stability condition}
%
We use $m$-reachability to encode the stability condition in VTSs.
%
The following constraint recursively encodes that node $j$ is $m$-reachable from node $i$ in less than $p$ steps
if either there is a direct edge between $i$ and $j$ with $m$ present on the edge or there is a edge between $i^{\prime \prime}$ and
$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
\begin{align*}
  \texttt{Paths}(r) &= \bigwedge\limits_{i,j,m,p} r_{i,j,m,p} \limplies (\bigvee_{q} \, e_{i,j,q,m} \lor \bigvee_{i\neq i^{\prime}} ( \, \bigvee_{q} e_{i,i^{\prime},q,m}) \land r_{i^{\prime},j,m,p-1} )
\end{align*}
Now we can encode stability using the reachability variables.
and say if there is an $m$-edge between $i$ and $j$, there is
$m$-reachable path from $j$ to $i$.
\begin{align*}
 \texttt{Loop}(r) &= \bigwedge\limits_{i,j,m} (\bigvee_{q} e_{i,j,q,m}) \limplies r_{j,i,m,\nu}
\end{align*}

@@

\subsubsection{$k$-connectivity constraints}
To check whether $k$-connected is a necessary condition, we remove (drop) $k-1$ edges from the graph and if it
disconnects the graph, and we get an assignment. We have a graph that is not  $k$-connected.
%
Constraints \texttt{Fail}(d,k), \texttt{FReach}(d,r') and \texttt{Connected}(r')
encode the relevant constraints for reachability
in the modified VTS. 
%
The following constraints encode that only
existing edges can be dropped and exactly $k-1$ edges are dropped.
\begin{align*}
\texttt{Fail}(d,k) = & 
\bigwedge\limits_{i,j,q} d_{i,j,q} \limplies e_{i,j,q}  \land 
\sum_{i,j,q} d_{i,j,q} = k-1\\
\end{align*}
We need to define reachability in the modified VTS, therefore we use
a new variable $r'_{i,j}$ to encode reachability from $i$ to $j$.
In the following constraint, we encode $r'_{i,j}$ is true if there is an
edge $(i,\_,j)$ and it is not dropped, or there is a node
$i^{\prime}$ such that, there is an edge $(i,\_,i^{\prime})$ which is
not dropped and $r'_{i',j}$ is true.
\begin{align*}
\texttt{FReach}(d,r') = &  \bigwedge\limits_{i,j}  [\bigvee_{q} (e_{i,j,q} \land  \neg d_{i,j,q}) \lor  (\bigvee_{i' \neq i}  r^{\prime}_{i',j} \land  \bigvee_{q} (e_{i,i',q} \land \neg d_{i,i',q}) ] \limplies r^{\prime}_{i,j}  
\end{align*}
Since we search for disconnected modified VTS,
the following constraint encodes that there are 
unreachable pair of nodes in the underlying undirected graph.
% nodes such that
% there is no path between them .
\begin{align*}
   \texttt{Connected}(r')  = & \bigvee\limits_{i,j} \neg (r^{\prime}_{i,j} \lor r^{\prime}_{j,i})
\end{align*}

@@

To specify the stability condition, we use nondeterminism to perform enumeration.
%
%Nondeterminism can be viewed as an oracle that guesses a correct path for a specific $m$ if it exists. 
%
%We then use this path as a witness to ensures that stability is maintained for each outgoing molecule $m$ on every edge $E$.
%
%
Note that the enumeration is done only for an unwinding depth $w$.
%
The encoding presented below is a simpler version of the implementation. 
\subsubsection{Constraints for stability condition}
%
A path between node $i$ and $j$ in the graph is a $m$-$path_{ij}$, if molecule $m$ is present on edges along that path.
%
%We use {\npath} to represent the required path to encode the stability condition in VTS.
%
%A naive implementation is shown in~\ref{eq:reachbmc1} where 
We use {\npath}$(m, i, j, w)$ to represent the presence of a $m$-$path_{ij}$ of maximum $w$ length.
%there is a edge between $i^{\prime \prime}$ and01
%$(i \neq i^{\prime \prime})$ with $m$ present, and j is $m$-reachable from $i'$ in less than $p-1$ steps.
%
% \begin{align}
%   NOracle (m, i, j, w) = \exists \, path[h1, ..., hn]: \\ 2 \leq |path| \leq  w + 2  \, \land h1 = i \, \land  hn = j \, \land \\ 
%   \bigvee\limits_{k = 1}^{|path|- 1} \bigvee\limits_{q}  E[hk] [hk+1][q][m] 
%   \tag{S1}\label{eq:reach1}
% \end{align}
%The NOracle can be thought of as a disjunction of $m$-path of increment length. 
%
$\npath(m, i, j, w)$ performs enumeration of every $m$-$path_{ij}$ of at most $w$ length. 
%
Starting with exploring $m$-${paths}_{ij}$ of length 1; a direct edge between $i$ and $j$ with molecule $m$ present, until every $m$-${paths}_{ij}$ of length $w-1$ is explored.
%by performing series of node hops till final node destination j is reached.
%Starting with $m$-${paths}_i^j$ of length 1 which is a direct edge between $i$ and $j$ with molecule $m$ present on the edge or performing series of node hops till final node destination j is reached.

@@

\begin{align*}
\npath(m, i, j, w) = \bigvee\limits_{l = 1}^{w-1} (\texttt{Length} (m-path_{ij}) == l)
\end{align*}

@@

\begin{align*}
	\bigwedge\limits_{i,j,m} (\bigvee_{q} (\texttt{bvEdge}[i][j][q] \unrhd m) == 1) \limplies \npath(m, j, i, w)
\end{align*}

### 2019-03-20 papers/journal/property.tex
First push for SMT QBF overlap

%\ankit{This section needs a revision}
We analyze the model against our desired properties.
%
Since in biology there are no declared specifications or properties,
we conjecture some properties that appear to be true in all the known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.

>>>>

\todo{This section needs a revision}
We analyze the model against our desired properties.
%
\ankit{Not completely correct}Since in biology there are no declared specifications or properties,
we conjecture some properties that appear to be true in all the known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.
